### 2017-04-09 README.Rmd
properly registered native routines
fixed URL

A detailed introduction to `pdp` has been accepted for publication in The R Journal; a preprint is available [here](https://github.com/bgreenwell/pdp-paper/blob/master/RJwrapper.pdf). You can track development on  at https://github.com/bgreenwell/pdp. To report bugs or issues, contact the main author directly or submit them to https://github.com/bgreenwell/pdp/issues.

>>>>

A detailed introduction to `pdp` has been accepted for publication in The R Journal; a preprint is available [here](https://journal.r-project.org/archive/2017/RJ-2017-016/index.html). You can track development on  at https://github.com/bgreenwell/pdp. To report bugs or issues, contact the main author directly or submit them to https://github.com/bgreenwell/pdp/issues.
